%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{Josh}{Hsu}
       {Software Engineer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{About}
    Josh Hsu
    HAO-CHE HSU
	Chiayi City
    Taiwan
	\href{joshsyu.tw@gmail.com}{joshsyu.tw@gmail.com}
	Skype ID: joshsyu
  \section{Languages}
    Bilingual Chinese/English
  \section{Programming}
    {\color{red} $\varheartsuit$} 
	C/C++, Python, Verilog, Golang, Assembly 
  \section{Technical Skills}
  \subsection{Platforms}
	Linux, FreeBSD, Qemu, Docker, VMware, VirtualBox
  \subsection{Tools}
	GNU tools, EDA tools, GDB, Basic network administer, Git, Latex, Markdown
  \subsection{Libraries}
	OpenCL, CUDA, Pthread, OpenMP, MPI, OpenCV, Jekyll, Hugo
  \subsection{Areas}
	Virtualization
	High Performance Computing
	Embedded System
\end{aside}

\section{Interests}

System software design, Embedded system development,
Virtualization, Architecture design, Digital IC design(CPU, ASIC), 
High performance computing, AI system(car)
\section{Education}

\begin{entrylist}
  \entry
    {Since \\
	 2015 Feb.}
    {Master, GPA: 4.1 / 4.3}
    {National Tsing Hua University, Hsinchu Taiwan}
	{Major in Computer Science \\
	Specialization in System Software \\
	Member of NTHU System Software Lab \\
	Advisor: Prof. Yeh-Ching Chung}
  \entry
    {2011 Sep. \\
	- 2015 Feb.}
    {Bachelor, GPA: 4.18 / 4.3}
    {National Chung Cheng University, Chiayi, Taiwan}
	{Major in Electrical Engineer \\
	Specialization in System on Chip \\
	Book Prize(7 times for 7 semesters)}
\end{entrylist}

\section{Experience}

\begin{entrylist}
  \entry
    {Since 2015}
    {HSAemu, Taiwan}
    {Master thesis, MOST project, MediaTek cooperative project}
    {\emph{System emulator of the new hardware architecture.} \\
	During a member of HSA foundation \\
	Based on Qemu and compatible with HSA specs}
  \entry
    {Since 2015}
    {PQEMU, Taiwan}
    {Master thesis}
    {\emph{A parallel and full software emulator}\\
	Parallize Qemu bonding to host threads}
  \entry
    {2015}
    {Family Monitoring Platform, Taiwan}
    {A small interesting project}
    {\emph{Video live streaming on website.} \\
	Based on embedded development board \emph{cubietruck}\\ 
	Use webcam as input streaming out to website(nginx, php)}
  \entry
    {Since 2015}
    {Github Pages, Taiwan}
    {My blog}
    {\emph{Static website development} \\
	Use markdown and Jekyll originally, porting Hugo now}
  \entry
    {2014 - 2015}
    {Face-tracking System, Taiwan}
    {Bachelor project.}
    {\emph{Face recognition.} \\ 
	Use OpenCV build-in module to train machine}
  \entry
	{2014}
	{Tetris on Microchip DISPIC33}
    {Bachelor project.}
    {\emph{Microchip development} \\
	Implment Tetris game on microchip and LCD output by C}
  \entry
    {2013}
	{Tiny Basic on 8051}
    {Bachelor project.}
    {\emph{Microchip development} \\
	Implement Tiny Basic Language on 8051 by assembly}
  \entry
    {2013 - 2014}
	{Vending Machine Controller Chip Design}
    {Bachelor project}
    {\emph{VLSI circuit design} \\
	Design controller from verilog to layout}
\end{entrylist}
%\section{Applications}
%\begin{entrylist}
%  \entry
%    {2015}
%    {HSA foundation}
%    {\href{http://www.hsafoundation.com/}{hsafoundation.com}}
%    {Member of HSA foundation.}
%  \entry
%    {2011}
%    {Fellows}
%    {\href{http://fellows-exp.com}{fellows-exp.com}}
%    {Automatic community detection among Facebook Friends in order to validate the \emph{cohesion} measure, creation of friend lists.}
%  \entry
%    {2008}
%    {Happy Flu}
%    {\href{http://happyflu.com}{happyflu.com}}
%    {Experiment aimed to measure viral spreading of content across the blogosphere.}
%\end{entrylist}

%\section{Publications}

%Put your publications here!
\begin{entrylist}
%	\entry
%	{2016}
%	{A Full HSA Development Platform}
%	{Conference Paper}
%	{CODE+ISSS \\
%	Author: Hao-Che Hsu}
%	\entry
%	{2016}
%	{HSAemu 2.0 with Soft-MMU and Parallel Devices}
%	{Master Thesis}
%	{Author: Hao-Che Hsu \\
%	Advisor: Yeh-Cheng Chung}

\end{entrylist}
%%% This piece of code has been commented by Karol Kozioł due to biblatex errors. 
% 
%\printbibsection{article}{article in peer-reviewed journal}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={international peer-reviewed conferences/proceedings}, notkeyword={france}, heading=subbibliography]
%\end{refsection}
%\begin{refsection}
%  \nocite{*}
%  \printbibliography[sorting=chronological, type=inproceedings, title={local peer-reviewed conferences/proceedings}, keyword={france}, heading=subbibliography]
%\end{refsection}
%\printbibsection{misc}{other publications}
%\printbibsection{report}{research reports}

\end{document}
